Viscous Transport in Eroding Porous Media

### 2019-06-14 docs/transport/erosion_transport.tex
do the tortuosity in transport paper
do the tortuosity in section 3 of transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transport, Tracers, and Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Erosion leads to interesting porous geometries, and we are interested in
characterizing transport in these geometries.  To characterize the
transport, we first require tracer trajectories (streamlines) that are
governed by
\begin{align}
  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
\end{align}
Instead of allowing the transport and erosion to happen simultaneously,
we freeze the geometry and compute the streamlines in this fixed
geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
we characterize the transport.

The tortuosity measures ...

{\color{red} the definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.

We define the local tortuosity
$$\tau(y)=\frac{\lambda(y)}{d}$$ 
of the tracers at $y$ on the starting cross section
where $\lambda(y)$ is the trajectory length of the tracer at y 
and $d$ is the distance from the starting cross section to 
the end cross section. }

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transport, Tracers, and Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Erosion leads to interesting porous geometries, and we are interested in
characterizing transport in these geometries.  To characterize the
transport, we first require tracer trajectories (streamlines) that are
governed by
\begin{align}
  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
\end{align}
Instead of allowing the transport and erosion to happen simultaneously,
we freeze the geometry and compute the streamlines in this fixed
geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
we characterize the transport.
{\color{red}
To study the interaction of fluid and fixed bodies in the porous media,
some parameters can be used to describle the interation quantitively,
for example the porosity, the permeability, and the tortuosity. 
The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
The definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
The tortuosity ...
{\color{red} represents the weighted average travel distance of a tracer in a porous media. 
The definition of tortuosity is 
$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
where $S$ is an arbitrary cross section which is perpendicular to the x axis,
$\lambda(y)$ is the length of streamline at y on $S$, 
$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
$d$ is the distance from $S$ to the end cross section.
It depends on not only the geometric structure but also the velocity of the fluid 
which is different from the porosity since porosity only depends on the geometric structure.}
{\color{red}Beisdes, the local tortuosity has been used to analysis 
the local behavior of steamline around a body
in~\cite{matyka2008tortuosity}.
The definition of local tortuosity of the tracers at $y$ on $S$ is
$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies 
when the porosity is 62.9 \% and the tortuosity is 1.0979.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies when the porosity is 62.98 \%
and the tortuosity is 1.1182.}
\end{figure}
